---
output: rmarkdown::github_document
---

# securitytxt

Identify and Parse Web Security Policies Files

## Description

When security risks in web services are discovered by independent
security researchers who understand the severity of the risk, they
often lack the channels to properly disclose them. As a result,
security issues may be left unreported. The 'security.txt' 'Web Security Policies'
specification defines a 'IETF' standard to help organizations define the process 
for security researchers to securely disclose security vulnerabilities. Tools are
provided to help identify and parse 'security.txt' files to enable analysis of 
the usage of these policies.

- [IETF Draft](https://tools.ietf.org/html/draft-foudil-securitytxt-00)
- [Information hub](https://securitytxt.org/)
- [GitHub Organization](https://github.com/securitytxt)

## What's Inside The Tin

The following functions are implemented:

- `sectxt`:	Parse a 'security.txt' Web Security Policies file & create a 'sectxt' object
- `sectxt_info`:	Retrieve a data frame of `security.txt` keys/values
- `sectxt_validate`:	Validate a 'security.txt' Web Security Policies file
- `sectxt_url`:	Determine `security.txt` URL for a given site/URL

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/securitytxt")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(securitytxt)

# current verison
packageVersion("securitytxt")

# built-in example
x <- sectxt(readLines(system.file("extdata", "security.txt", package="securitytxt")))
sectxt_info(x)

# "live" example
(xurl <- sectxt_url("https://securitytxt.org"))
x <- sectxt(url(xurl))
sectxt_info(x)
sectxt_validate(x)
x

# another "live" example
(xurl <- sectxt_url("https://rud.is/b"))
x <- sectxt(url(xurl))
sectxt_info(x)
sectxt_validate(x)
x

```

